{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
Some text changes

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method such as Cross-Validation. The influence of this truncation on the prediction accuracy of different estimates is the subject of the simulation study. {\color{red} Add text for figure}

	\begin{figure}[H]
		\includegraphics[width=\textwidth]{../Graphics/basis_expansions.pdf}
		\caption{B-spline Approximations of NIR Absorption Spectra with different Basis Truncation Parameters}
	\end{figure}

@@

	\subsection{Scalar-on-Function Regression}
	In the simple scalar setting, one of the most important tools in econometrics is linear regression. Its goal is to predict the value of a dependent variable given a set of associated variables. For reference, assume a data generating process as follows.

@@

	Where $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
	In this finite dimensional setting one important question is how to estimate the unknown coefficients $\beta$. The most well known estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.

@@

	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is supposed to be predicted from a functional variable. 
	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects. Therefore, we will always assume a data generating process as follows in this paper.

@@

	Where $\beta(t)$ is an unknown coefficient function. Similar to the finite-dimensional setting, an interesting question is how to estimate $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite-dimensional objects is not possible. Therefore, other options have to be considered.

@@

	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on what is possibly a countably infinite sequence of regressors. Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.

@@

	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects

>>>>

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method such as Cross-Validation. Figure \ref{Different_Expansions} shows the effect of choosing different truncation parameters for the case of the Near-Infrared Spectroscopy dataset which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the parameter choice.

	\begin{figure}[H]
		\includegraphics[width=\textwidth]{../Graphics/basis_expansions.pdf}
		\caption{B-spline Approximations of NIR Absorption Spectra with different Basis Truncation Parameters}
		\label{Different_Expansions}
	\end{figure}

@@

	\subsection{Scalar-on-Function Regression}
	In the simple scalar setting, one of the most important tools in econometrics is linear regression. Its goal is twofold: to gain information about the dependency between variables, but also to allow for prediction. To motivate the jump from multivariate regression to scalar-on-function regression, assume first a data generating process as follows.

@@

	Here, $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
	In this finite dimensional setting one important question is how to estimate the unknown coefficients $\beta$. The most well known estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.

@@

	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is assumed to be dependent of a functional regressor. 
	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects. Therefore, we will always assume a data generating process as follows in this paper.

@@

	Here, $\beta(t)$ is an unknown coefficient function. Similar to the finite-dimensional setting, an interesting question is how to estimate $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite-dimensional objects is not possible. Therefore, other options have to be considered.

@@

	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on what is possibly a countably infinite sequence of regressors. Using a truncation of the basis at some parameter $J$ can be used to make this problem tractable if we assume that the approximation error created by this truncation is small.

@@

	A model in the form of Equation \ref{simplified_model_basis_equation} naturally lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects
